\thesistitle

### 2019-06-11 sections/research.tex
Overall type related stuff

\subsection{Type 1 clones} \label{chap:type1clones}
Type 1 clones are identical clone fragments except for variations in whitespace and comments \cite{roy2007survey}. This allows for the detection of clones that are the result of copying and pasting existing code, along with other reasons why duplicates might get into a codebase.

@@

\subsection{Type 2 clones}
Type 2 clones are structurally/syntactically identical fragments except for variations in identifiers, literals, types, layout and comments \cite{roy2007survey}. This definition allows for the reasoning about code fragments that were copied and pasted, and then slightly modified. The two methods displayed in figure \ref{fig:type2} are type 2 clones of each other.

@@

Looking at the example in listing \ref{lst:type2clones}, we see an example of a type 2 clone that poses no harm to the system whatsoever. Both methods are, except for their matching structure, completely different in functionality. They operate on different types, call different methods, return different things, etc. Having such a method flagged as a clone does not provide any useful information.

@@

\section{Refactoring-oriented clone types}
To resolve the shortcomings of clone types as outlined in the previous section, we propose alternative definitions for clone types to be directed at detecting clones that can and should be refactored. We have named these clones type 1R, 2R and 3R clones. These definitions share similarities with the literature definitions, thus the usage of . The ``R'' stands for refactoring-oriented (and may be less suitable for other analyses).

@@

\subsubsection{Referenced Types}
Many object-oriented programming languages (like Java, Python, C#) require the programmer to import a type (or the class in which it is declared) before it can be used. Based on what is imported, the meaning of the name of a type can differ. For instance, if we import \texttt{java.util.List}, we get the interface which is implemented by all list datastructures in Java. However, importing \texttt{java.awt.List}, we get a listbox GUI component for the Java Abstract Window Toolkit (AWT). Because of this, for type 1R clones, we compare the fully qualified identifier for all referenced types.

@@

\subsubsection{Variables}
In typed programming languages, each variable declaration should declare a name and a type. When we reference a variable, we only use its name. If, in different code fragments, we use variables with the same name but different types, the code can be functionally unequal but still textually equal. As an example, see the code in listing \ref{lst:type2variables}.

\begin{lstlisting}[caption={Variables with different types but the same name.},label={lst:type2variables},language=Java]
public String appendFive(String x){
	return x + 5;
}

public int addFive(int x){
	return x + 5;
}
\end{lstlisting}

The body of both methods in listing \ref{lst:type2variables} is equal. However, their functionality is not.

@@

\section{Considering several types}
In this chapter we have proposed refactoring-oriented definitions using the type 1, 2 and 3 clone definitions from literature as a baseline. In literature, these definitions are mainly aimed towards reasoning about duplication in source code. When considering these types for refactoring, the goal becomes slighly different. Because of this, having separate clone type definitions does not have any value. Rather, we need a single clone type definition

>>>>

\subsection{Type 1 clones} \label{chap:type1clones}
Type 1 clones are \textit{identical clone fragments except for variations in whitespace and comments} \cite{roy2007survey}. This allows for the detection of clones that are the result of copying and pasting existing code, along with other reasons why duplicates might get into a codebase.

@@

\subsection{Type 2 clones}
Type 2 clones are \textit{structurally/syntactically identical fragments except for variations in identifiers, literals, types, layout and comments} \cite{roy2007survey}. This definition allows for the reasoning about code fragments that were copied and pasted, and then slightly modified. The two methods displayed in figure \ref{fig:type2} are type 2 clones of each other.

@@

Looking at the example in listing \ref{fig:type2}, we see an example of a type 2 clone that poses no harm to the design of the system. Both methods are, except for their matching structure, completely different in functionality. They operate on different types, call different methods, return different things, etc. Having such a method flagged as a clone does not provide much useful information.

@@

\subsection{Type 3 clones}
Type 3 clones are \textit{copied fragments with further modifications. Statements can be changed, added or removed in addition to variations in identifiers, literals, types, layout and comments} \cite{roy2007survey}. Detection of clones by this definition can be very hard, as it may be hard to detect whether a fragment was copied in the first place if it was severely changed. Because of this, most clone detection implementations of type 3 clones work on basis of a similarity threshold \cite{svajlenko2014evaluating, cordy2011nicad}. This similarity threshold has been implemented in different ways: textual similarity (for instance using levenshtein distance) \cite{lavoie2011automated}, token-level similarity of statement-level similarity.

Having a definition that allows for any change in code poses serious challenges on refactoring. A levenshtein distance of one can already change the meaning of a code fragment significantly, for instance if the name of a type differs by a character (and thus referring to different types).

\section{Refactoring-oriented clone types}
To resolve the shortcomings of clone types as outlined in the previous section, we propose alternative definitions for clone types to be directed at detecting clones that can and should be refactored. We have named these clones type 1R, 2R and 3R clones. These definitions share similarities with the literature definitions, the number of each type corresponds with the clone type it is modeled after. The ``R'' stands for refactoring-oriented (and may be less suitable for other analyses).

@@

\subsubsection{Referenced Types}
Many object-oriented programming languages (like Java, Python, C\#) require the programmer to import a type (or the class in which it is declared) before it can be used. Based on what is imported, the meaning of the name of a type can differ. For instance, if we import \texttt{java.util.List}, we get the interface which is implemented by all list datastructures in Java. However, importing \texttt{java.awt.List}, we get a listbox GUI component for the Java Abstract Window Toolkit (AWT). Because of this, for type 1R clones, we compare the fully qualified identifier for all referenced types.

@@

\subsubsection{Variables}
In typed programming languages, each variable declaration should declare a name and a type. When we reference a variable, we only use its name. If, in different code fragments, we use variables with the same name but different types, the code can be functionally unequal but still textually equal. As an example, see the code in figure \ref{lst:type1variables}.

\begin{figure}[H]
  \includegraphics[width=1\columnwidth]{img/type2}
  \caption{Variables with different types but the same name.}
  \label{fig:type1variables}
\end{figure}

The body of both methods in figure \ref{lst:type2variables} is equal. However, their functionality is not. The first method adds two numbers together and the other concatenates an integer to a String.

For type 1R clones variable references should be compared by both type and name.

@@

\section{Unifying the types}
In this chapter we have proposed refactoring-oriented definitions using the type 1, 2 and 3 clone definitions from literature as a baseline. In literature, these definitions are mainly aimed towards reasoning about duplication in source code. When considering these types for refactoring, the goal becomes slighly different. Because of this, having separate clone type definitions does not have any value. Rather, we need a single clone type definition by which we can detect all clones that can and should be considered for refactoring.

Because of this, the ultimate goal would be not to consider type 1R, 2R and 3R separately, but together. However, this is dependent on good thresholds for the type 2R variability and type 3R gap size. Because of this, we have dedicated section \ref{sec:thresholds} to performing measurements to find good thresholds. The ultimate goal is to have a single unified definition of clones that can and should be refactored. Although it will be next to impossible to define such a definition and its corresponding thresholds that does not detect false positives. However, we strive to find at least a near-optimal set of thresholds regarding the type definitions proposed in this chapter.
